---
title: "rbtl-fs22 end-of-semester exam"
subtitle: "Section 01"
format: html
execute: 
  eval: false
editor: visual
editor_options: 
  chunk_output_type: console
---

# Points

The maximum number of points for this section is: **12 out of 50**. The number of points for each task is shown in parenthesis next to the task number.

# Task 1.0 (0.5)

1.  Render the document and fix any errors.

```{r}
#| eval: true
library(tidyverse)
```

# Task 1.1 (1)

**Fill in the blanks**

1.  Use the `read_csv` function to import the following two CSV files from the "data/what_a\_waste/" directory:

-   `what-a-waste-city-level-data.csv`, and assign to the object `city_data`
-   `what-a-waste-city-level-data-distance.csv`, and assign to the object `distance`

```{r}

city_data <- ___(___) 

distance <- ___(___) 

```

# Task 1.2 (1)

**Fill in the blanks**

1.  Start with the `city_data` object and use the `select()` function to create a subset that only keeps the following variables:

-   city
-   income_id
-   all variables that start with "waste"

```{r}

___ %>% 
  select(___) 

```

# Task 1.3 (1.5)

**Fill in the blanks**

1.  Start with the `city_data` object and use the `select()` function to create a subset that only keeps the following variables:

-   city
-   income_id
-   all variables that contain the word string "distance"
-   not transportation_distance_na

```{r}

city_data ___
  select(___) 

```

# Task 1.4 (1)

**Fill in the blanks**

1.  Start with the `distance` object and use a function of your choice to create a subset that removes NAs from the variable which stores values for the total transporation distance in km/year.

2.  Store the subset as a new object in your environment with the name `distance_complete`

```{r}

distance_complete <- ___ %>% 
  ___(___) 

```

# Task 1.5 (1)

**Fill in the blanks**

1.  Start with the `distance_complete` object and use the `arrange()` function to display the 'transporation_distance_disposal_site' variable in descending order.

```{r}

distance_complete %>% 
  ___(___) 

```

# Task 1.6 (2.5)

**Fill in the blanks**

1.  Use the `mutate()` function to add a new column to `distance_complete` that is the number of trips per day. Name the column `trips_day`.

2.  Use the pipe operator to add another line of code which uses the `mutate()` function to add a new column that is the number of trips per 1000 people and day. Name the column `trips_1000_ppl_day`.

3.  Store the result as a new object in your environment with the name `distance_complete_extended`

```{r}

distance_complete_extended <- distance_complete %>% 
  ___(trips_day = transportation_distance_total_km_year / transporation_distance_disposal_site / ___) %>%
  ___(trips_1000_ppl_day = trips_day / ___ * ___) 

```

# Task 1.7 (1)

**Fill in the blanks**

1.  Use the `filter()` function to create a subset from `distance_complete_extended` containing observations for cities where the number of trips per 1000 people and day is between 1 (inclusive) and 2 (not inclusive).

```{r}

distance_complete_extended %>% 
  ___(___) 

```

# Task 1.8 (2)

1.  Edit the YAML header to add your name to be displayed as the author of this document in the rendered HTML file.

2.  Edit the YAML header with options to display a table of contents in the rendered HTML file.

3.  Edit the YAML header to not display warnings in the rendered HTML file.

4.  Edit the YAML header to change value at `eval:` from `false` to `true`.

# Task 1.9 - Hand-in (0.5)

1.  Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.
