---
title: "rbtl-fs22 end-of-semester exam"
subtitle: "Section 03"
format: html
editor: visual
execute: 
  echo: true
  warning: false
editor_options: 
  chunk_output_type: console
---

# Points

The maximum number of points for this section is: **12 out of 50**. The number of points for each task is shown in parenthesis next to the task number.

# Task 3.0 (0.5)

1.  Render the document and fix any errors.

```{r}
library(tidyverse)
```

```{r}

treatment <- read_csv("data/what_a_waste/what-a-waste-city-level-data-treatment.csv")

```

# Task 3.1 (1.5)

1.  Starting with the `treatment` data object, use functions taught during the course to answer the following question:

How many cities are covered in this dataset? 199 cities

```{r}



```

# Task 3.2 (2)

1.  Starting with the `treatment` data object, use functions taught during the course to answer the following question:

Which country has the greatest number of cities in the dataset, and how many cities is that? India with 420 cities

```{r}



```

# Task 3.3 (1.5)

1.  Starting with the `treatment` data object, use functions taught during the course to answer the following question:

In how many countries is all waste (100%) openly dumped? 27 cities

```{r}


```

# Task 3.4 (2)

1.  Starting with the `treatment` data object, use functions taught during the course to answer the following question:

How many cities in which no waste (0%) is recycled fall into each income category?

```{r}



```

# Task 3.5 (4)

1.  Starting with the `treatment` data object, use functions taught during the course to answer the following question:

What is the mean, median, and standard deviation of treatment percentages for each waste treatment option and grouped by income?

```{r}



```

# Task 3.6 - Hand-in (0.5)

1.  Render the document and fix any errors.

Last complete render: `r Sys.time()` at timezone `r Sys.timezone()`.
